---
title: "Social Survey"
author: "Kevin Reyes"
date: "April 24, 2018"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# SEX

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
```{r}
source("makeTables2016.R")
barchartGC(xsex_sex,type="percent")
```

Make Comments about male and females have opposing opinions 
```{r}
chisqtestGC(xsex_sex, graph=TRUE)
```
Reject The null hypothesis.

```{r}
rowPerc(xsex_sex)
colPerc(xsex_sex)
```


#Polyviews

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



#Relationship status



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->---
title: "Social Survey"
author: "Kevin Reyes"
date: "April 24, 2018"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# SEX

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
```{r}
source("makeTables2016.R")
barchartGC(xsex_sex,type="percent")
```

After constructing a barchart from the data for views on extra marital sex, it appears that both sexes have different views. Females are more likely, than men, to believe that extra marital sex is wrong. Men are slightly more likely, than females, to be on the fence about extra martial sex. Additionally men are more likely, than females, to believe extra marital sex is ok.

```{r}
chisqtestGC(xsex_sex, graph=TRUE)
```
Our p-value from the ChiSquared test is 0.0351. This suggests that, under a true null hypothesis, we have about a 3% probablity of returning a sample like this. The p-value must exceed 5%, in order to accept our null hypothesis as true, so we will reject the null hypothesis. Therefore, there is not a relationship between sex and belief on extra marrital sex.

```{r}
rowPerc(xsex_sex)
```
In the group of who think extra merital sex is <b>wrong</b>, 43.11% of men think extra marital sex is <b>wrong</b>, and so do 56.89% of females.

In the group who are <b>not sure</b> about extra merital sex, 51.55% of men are <b> not sure</b>, and 48.45% of females are too.

In the group who think extra marital sex is <b>ok</b> 54.90% of men think its <b>ok</b> and 45.10% of females aslo do.

```{r}
colPerc(xsex_sex)
```
In the group of who think extra merital sex is <b>wrong</b>, 86.53% of ALL men think extra marital sex is <b>wrong</b>, and so did 90.31% of the ALL females.

In the group who are not sure about extra merital sex, 10.07% of ALL men are <b> not sure</b>, and so were 7.49% of ALL females are too.

In the group who think extra marital sex is <b>ok</b> 3.40% of ALL men think its <b>ok</b> and 2.21% of ALL females aslo do.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In this study we concluded that there is no relationship between sex and views on extra marital sex. In the process, we created a barchart to graphically map the data and see the relationship in the data. In the barchart, we saw that men and women differ in each category. After, we ran an inferrential test to determine if there is a relationhsip, we used the chisquared test. The test gave us a p-value of of about 3, so we rejected the null hypothesis, and concluded that there is no relationsip between sex and views on extra marital sex. Next, we created row perecents, to compare the percentages of how men and women voted in each category. Finally, we also created row percentages to see what did all the men vote for and all the women. 